Append_smoothed_results

### 2016-11-23 Code/append_smoothed_results.Rmd
calculate proportion contribution

       list.cod.marginal.tables.smoothed[[i]] <- list.cod.decomp.tables.smoothed[[i]] %>% 
                                                  group_by(Cause.of.death) %>% 
                                                  summarise(C_x_COD = sum(C_xi))

>>>>

       list.cod.marginal.tables.smoothed[[i]] <- list.cod.decomp.tables.smoothed[[i]] %>% 
                                                  group_by(Cause.of.death) %>% 
                                                  summarise(C_x_COD = sum(C_xi)) %>%
                                                  mutate(C_x_COD_proportion = C_x_COD/sum(C_x_COD))
